Phenology and Mycorrhizae Manuscript

### 2023-02-17 manuscriptCode_phenologyAndMycorrhizae.Rmd

for(f in seq_along(funTypes)){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
}

@@

>>>>

for(f in seq_along(funTypes)){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName[f])
}

@@

for(f in seq_along(funNames)){
  print(funNames[f])
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
    gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
}
```
